Pure Spin Current Injection in Hydrogenated Graphene Structures

### 2017-05-09 mu/article/article.tex
Description almost finished
There is only needed to chewck in the articles the meaning of a -
sign for V^{ab} and make a description of the non centrocym

{\color{red}
\subsection{Pure spin velocity} % (fold)
\label{sec:theory-pure_spin_current}

@@

Now we define the spin velocity, $\mathcal{V}^{\mathrm{ab}}$ as the speed at
which the spin polarized in the $\mathrm{b}$   direction moves along the
$\mathrm{a}$ direction when a normal incident beam reaches the $xy$ plane with a
polarization angle $\alpha$. Then,
} % COLOR RED END
\begin{widetext}
\begin{align}
\mathcal{V}^{\mathrm{ab}} (\omega) 
&= \frac{2}{\hbar}
\frac{\mu^{\mathrm{abxx}}(\omega)
E^{2}(\omega)\cos^{2}(\alpha) + 
\mu^{\mathrm{abyy}}(\omega)
E^{2}(\omega)\sin^{2}(\alpha) + 
2\mu^{\mathrm{abxy}}(\omega)
E^{2}(\omega)\cos(\alpha)\sin(\alpha)}
{\xi^{\mathrm{xx}}(\omega)
E^{2}(\omega)\cos^{2}(\alpha) + 
\xi^{\mathrm{yy}}(\omega)
E^{2}(\omega)\sin^{2}(\alpha)},
\nonumber \\
&= \frac{2}{\hbar}
\frac{\mu^{\mathrm{abxx}}(\omega)\cos^{2}(\alpha) + 
\mu^{\mathrm{abyy}}(\omega)\sin^{2}(\alpha) + 
\mu^{\mathrm{abxy}}(\omega)\sin(2\alpha)}
{\xi^{\mathrm{xx}}(\omega)\cos^{2}(\alpha) + 
\xi^{\mathrm{yy}}(\omega)\sin^{2}(\alpha)}.
\label{eq:vab}
\end{align}
\end{widetext}

@@

{\color{red}
\subsection{Layer-by-layer analysis.}\label{sec:theory-layer}

@@

} % COLOR RED END

@@

Using the ABINIT code \cite{gonzeCPC09} we calculated the self-consistent ground
state and the Kohn-Sham states using density functional theory in the local
density approximation (DFT-LDA) with a planewave basis. We used Hartwigsen-
Goedecker-Hutter (HGH) relativistic separable dual-space Gaussian
pseudopotentials \cite{hartwigsenPRB98} including the spin-orbit interaction
\textcolor{red}{ needed to calculate $\mu^{\mathrm{abcd}}(\omega)$ (Eq.
\eqref{eq:mu}) and $|\mathcal{V}^{\mathrm{a}}(\omega)|$ (Eq. \eqref{eq:vab}).}
%
{\color{red} 
It is known that using DFT-LDA to calculate the electronic structure of
materials predict a different band gap than the obtained experimentally. A
correction for the band gap energy value can be calculated by other \emph{ab-
initio} methods such as the GW approximation \cite{onidaRMP02} but this is
outside the scope of this paper.
} % COLOR RED END
% 
The convergence parameters for the calculations of our results corresponding to
the \emph{alt} and \emph{up} structures are cutoff energies of 65\,Ha and
40\,Ha, respectively. The energy eigenvalues and matrix elements were calculated
using 14452 $\mathbf{k}$ points and 8452 $\mathbf{k}$ points in the irreducible
Brillouin zone (IBZ) and present LDA energy band gaps of 0.72\,eV and 0.088\,eV,
respectively for the \emph{alt} and \emph{up} structures.

@@

{\color{red}

@@

\caption{\color{red} Comparison of the reported maxima values of
$\mathcal{V}^{\mathrm{ab}}$ for different structures and the corresponding
polarization angle $\alpha$ and energy values.}
\label{tab:vab-str-comp}
\end{table}

@@

In figure \ref{fig:vab-str-comp} we present a comparison of the most intense
responses resulting from evaluate the Eq. \eqref{eq:vab} for the \emph{alt} and
\emph{up} 2D structures vs. CdSe and GaAs bulk structures. As we can see from
this figure the most intense response corresponds to the \emph{up} structure
centered at 0.088\,eV corresponding to the terahertz radiation and reaching a
spin velocity of 87.16\,Km/s.
% 
In the other hand, for an energy range from 0.66\,eV to 3.0\,eV all the
four structures have contributions in the same order of magnitude. 
% 
Starting with the 2D structures we have that the \emph{up} structure has other
two peaks centered at 1.94\,eV and 1.97\,eV reaching spin velocities of
22.2\,Km/s and -29.7\,Km/s, respectively, and the \emph{alt} structure has two
peaks centered at 0.72\,eV and 0.91\,eV reaching spin velocities of -40.2\,Km/s
and -32.9\,Km/s, respectively.
% 
Then, for the bulk structures we have that the CdSe has only one intense
response centered at 0.91\,eV reaching a spin velocity of -26.9\,Km/s, and the
GaAs structure has a large and almost planar zone where the response is held
reaching the maximum for an incoming beam of energy of 2.31\,eV and reaching a
spin velocity of -21.6\,Km/s.
% 
In table \ref{tab:vab-str-comp} we present the comparison of this values for the
2D and bulk structures.
% 
} % COLOR RED END

@@

    \caption{\color{red} $|\mathcal{V}_{\sigma^{\mathrm{z}}}|(\omega)$, response
    vs. photon energy vs. polarization angle $\alpha$ for the \emph{up}
    structure for two energy ranges. The absolute maxima is located for an
    energy range from 0.08\,eV to 0.10\,eV and the local maximum from 1.95\,eV
    to 2.0\,eV and both for polarization angles between $25^{\circ}$ and
    $50^{\circ}$.}
    \label{fig:up-3d-vsz}
\end{figure}

\begin{figure}[b]
    \centering
    \subfigure[\, \label{fig:up-vaz-rag-1}]
    {\includegraphics[width=\linewidth]{upplots/up-vaz-rag-1}}
    \\
    \subfigure[\, \label{fig:up-vaz-rag-2}]
    {\includegraphics[width=\linewidth]{upplots/up-vaz-rag-2}}

    \caption{\color{red} Most intense response of
    $|\mathcal{V}_{\sigma^{\mathrm{z}}}|(\omega)$ (top frames, right scale of
    figs (a) and (b)), the corresponding velocity angle
    $\gamma_{\mathrm{z}}(\omega)$ (top frames, right scale), the collinear
    (circled box) and perpendicular (square box) angles, and the two components
    $\mathcal{V}^{\mathrm{xz}}(\omega)$ and $\mathcal{V}^{\mathrm{yz}}(\omega)$
    (bottom frames) for the \emph{up} structure fixing the energy to 0.088\,eV.
    }
    \label{fig:up-vaz-rag}
\end{figure}

We first present two energy ranges for the \emph{up} structure, the first for an
incoming energy beam from 0.0\,eV to 0.2\,eV where the absolute maximum of the
$|\mathcal{V}_{\sigma^{\mathrm{z}}}|(\omega)$ response is obtained and the
second for an energy range from 1.80\,eV to 2.1\,eV where two local maxima are
found.
% 
In Fig. \ref{fig:up-3d-vsz} we present the
$|\mathcal{V}_{\sigma^{\mathrm{z}}}|(\omega)$ spectra resulting from evaluate
the Eq. \eqref{eq:vs-mag} using different polarization angles $\alpha$ in the
Eq. \eqref{eq:vab} for the \emph{up} structure. In the figure we have that the
onset of the response starts when the energy of the incoming beam is the same of
the gap energy.
% 
From this figure we obtained that the zone where the maximum response is held
corresponds to a energy range of the incident beam from 0.084\,eV to 0.093\,eV
and polarization angles $\alpha$ between $30^{\circ}$ and $45^{\circ}$. Also two
local maxima are held for same polarization angles but for an energy range of
the incoming beam between 1.90\,eV and 2.05\,eV.
% 
In the top frames of Figs.\ref{fig:up-vaz-rag-1} and \ref{fig:up-vaz-rag-2} we
present in solid lines the result of evaluate
$|\mathcal{V}_{\sigma^{\mathrm{z}}}|(\omega)$, related to the left scale, fixing
the energy of the incoming beam to 0.088\,eV and 0.912\,eV, respectively, for
which the response is maximized for the \emph{up} structure. In the same figures
and frames we present in dashed lines, related to the right scale, the
corresponding velocity angle $\gamma_{\mathrm{z}}(\omega)$ and in the bottom
frames of those figures the corresponding components
$\mathcal{V}^{\mathrm{xz}}(\omega)$ and $\mathcal{V}^{\mathrm{yz}}(\omega)$.
Also we present two circled and square boxes indicating the value where the
angles of the spin velocity is parallel and perpendicular and the the
corresponding arrows is directed to the value of the response corresponding to
those angles.

@@

\begin{figure}[tb]
    \centering
    \includegraphics[width=\linewidth]{altplots/alt-3d-svaz}
    \caption{\color{red} $|\mathcal{V}_{\sigma^{\mathrm{z}}}|(\omega)$, response
    vs. photon energy vs. polarization angle $\alpha$ for the \emph{alt}
    structure. The absolute maximum is located for an energy range from 0.90\,eV
    to 0.93\,eV and for polarization angles between $120^{\circ}$ and
    $150^{\circ}$.}
    \label{fig:alt-3d-vsb}
\end{figure}

\begin{figure}[t]
    \centering
    \includegraphics[width=\linewidth]{altplots/alt-vaz-rag}
    \caption{Most intense response of
    $|\mathcal{V}_{\sigma^{\mathrm{z}}}|(\omega)$ (top frame, left scale) the
    corresponding velocity angle $\gamma_{\mathrm{z}}(\omega)$ (top frame, right
    scale), the collinear (circled box) and perpendicular (square box) angles,
    and the two components $\mathcal{V}^{\mathrm{xz}}(\omega)$ and
    $\mathcal{V}^{\mathrm{yz}}(\omega)$ (bottom frame) for the \emph{alt}
    structure fixing the energy to 0.912\,eV.}
    \label{fig:figure1}
\end{figure}

For the \emph{alt} structure we present the energy range of the incoming beam from 0.6\,eV to 1.0\,eV, where the absolute and a local maxima of the
$|\mathcal{V}_{\sigma^{\mathrm{z}}}|(\omega)$ response are obtained.
% 
In Fig. \ref{fig:alt-3d-vsb} we present the
$|\mathcal{V}_{\sigma^{\mathrm{z}}}|(\omega)$ spectra resulting from evaluate
again the Eq. \eqref{eq:vs-mag} using different polarization angles $\alpha$ in
the Eq. \eqref{eq:vab} for the \emph{alt} structure. In the figure we have that
the onset of the response starts when the energy of the incoming beam is the
same of the gap energy.
% 
From this figure we obtained that the zone where the absolute maximum response
is held corresponds to a energy range of the incident beam from 0.90\,eV to
0093\,eV and polarization angles $\alpha$ between $120^{\circ}$ and
$150^{\circ}$. The local maximum is held or the same polarization angles but for
energies between 0.67\,eV and 0.75\,eV.

@@

\textbf{Up structure.}
% %%%%%%%%%%%%%%%%%
% %% 0.0 eV - 0.16 eV
% %% Description of UP |V^{a}| 3D
% %% files: 
% %% magv.sm_0.03_xb_12802_40-spin_scissor_0_Nc_32_incang_0-180-step5
% %% magv.sm_0.03_yb_12802_40-spin_scissor_0_Nc_32_incang_0-180-step5
% %% up-3d-vab.gp
% %%%%%%%%%%%%%%%%%
\begin{figure}[t]
    \centering
    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|(\omega)$ for \emph{up} structure
    \label{fig:up-3d-vvx-1}]
    {\includegraphics[width=\linewidth]{upplots/up-3d-vxb-1}}
    \\
    \subfigure[\ $|\mathcal{V}^{\mathrm{y}}|(\omega)$ for \emph{up} structure
    \label{fig:up-3d-vvy-1}]
    {\includegraphics[width=\linewidth]{upplots/up-3d-vyb-1}}

@@

For the \emph{up} structure we first analyzed the energy range from 0.00\,eV to
0.16\,eV where we found the most intense response and the absolute maxima for
$|\mathcal{V}^{\mathrm{x}}|(\omega)$ and $|\mathcal{V}^{\mathrm{y}}|(\omega)$.
% 
In Fig. \ref{fig:up-3d-vva-1} we present the
$|\mathcal{V}^{\mathrm{a}}|(\omega)$ spectra resulting from evaluate the Eq.
\eqref{eq:vv-mag} using different polarization angles $\alpha$ in the Eq.
\eqref{eq:vab} for the \emph{up} structure. We can see that the onset of the
response is when the energy of the incoming light is the same of the gap energy.
%
From this picture we can see that for the zone between the energy range of
0.084\,eV-0.093\,eV and polarization angles between $30^{\circ}$ and
$45^{\circ}$ is the zone where the maximum response is held for both,
$|\mathcal{V}^{\mathrm{x}}|(\omega)$ and $|\mathcal{V}^{\mathrm{y}}|(\omega)$.
% %%%%%%%%%%%%%%%%%
% %% 1.8 eV - 2.0 eV
% %% Description of UP |V^{a}|, components and RTP
% %% files: 
% %% vab-rtp.sm_0.03_x_12802_40-spin_scissor_0_Nc_32_ang_040
% %% vab-rtp.sm_0.03_y_12802_40-spin_scissor_0_Nc_32_ang_040
% %% up-3d-vab.gp
% %%%%%%%%%%%%%%%%%

@@

% %% files: 
% %% vab-rtp.sm_0.03_x_12802_40-spin_scissor_0_Nc_32_ang_040
% %% vab-rtp.sm_0.03_y_12802_40-spin_scissor_0_Nc_32_ang_040
% %% up-3d-vab.gp

@@

% %% files: 
% %% magv.sm_0.03_xb_12802_40-spin_scissor_0_Nc_32_incang_0-180-step5
% %% magv.sm_0.03_yb_12802_40-spin_scissor_0_Nc_32_incang_0-180-step5
% %% up-3d-vab.gp

@@

1.80\,eV to 2.10\,eV presented in Fig. \ref{fig:up-3d-vva-2} where two local
maxima of $|\mathcal{V}^{\mathrm{x}}|(\omega)$ and
$|\mathcal{V}^{\mathrm{y}}|(\omega)$ are obtained for the \emph{up} structure.

@@

% %% files: vab-rtp.sm_0.03_x_12802_40-spin_scissor_0_Nc_32_ang_040
% %%        vab-rtp.sm_0.03_y_12802_40-spin_scissor_0_Nc_32_ang_040
% %%        alt-plots/up-vab-rtp.gp

@@

\textbf{Alt structure.}
% %%%%%%%%%%%%%%%%%
% %% Description of ALT |V^{a}| 3D
% %% files: 
% %% magv.sm_0.03_xb_14452_65-spin_scissor_0_Nc_32_incang_0-180-step5
% %% magv.sm_0.03_yb_14452_65-spin_scissor_0_Nc_32_incang_0-180-step5
% %% alt-3d-vab.gp
% %%%%%%%%%%%%%%%%%
\begin{figure}[tb]
    \centering
    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|$ for \emph{alt} structure 
    \label{fig:alt-3d-vvx}]
    {\includegraphics[width=\linewidth]{altplots/alt-3d-vxb}}
    \\
    \subfigure[\ $|\mathcal{V}^{\mathrm{y}}|$ for \emph{alt} structure 
    \label{fig:alt-3d-vvy}]
    {\includegraphics[width=\linewidth]{altplots/alt-3d-vyb}}

@@

@@

1.0\,eV where we found the a local maxima and the most intense responses for
$|\mathcal{V}^{\mathrm{x}}|(\omega)$ and $|\mathcal{V}^{\mathrm{a}}|(\omega)$.
In Fig. \ref{fig:alt-3d-vva} we present the $|\mathcal{V}^{\mathrm{a}}|(\omega)$
spectra resulting from evaluate again Eq. \eqref{eq:vv-mag} using different

>>>>

\subsection{Pure spin velocity} % (fold)
\label{sec:theory-pure_spin_current}

@@

Now we define the spin velocity, $\mathcal{V}^{\mathrm{ab}}$ as the speed at
which the spin polarized in the $\mathrm{b}$   direction moves along the
$\mathrm{a}$ direction when a normal incident beam reaches the $xy$ plane with a
polarization angle $\alpha$. Then,
\begin{widetext}
\begin{align}
\mathcal{V}^{\mathrm{ab}} (\omega) 
&= \frac{2}{\hbar}
\frac{\mu^{\mathrm{abxx}}(\omega)
E^{2}(\omega)\cos^{2}(\alpha) + 
\mu^{\mathrm{abyy}}(\omega)
E^{2}(\omega)\sin^{2}(\alpha) + 
2\mu^{\mathrm{abxy}}(\omega)
E^{2}(\omega)\cos(\alpha)\sin(\alpha)}
{\xi^{\mathrm{xx}}(\omega)
E^{2}(\omega)\cos^{2}(\alpha) + 
\xi^{\mathrm{yy}}(\omega)
E^{2}(\omega)\sin^{2}(\alpha)},
\nonumber \\
&= \frac{2}{\hbar}
\frac{\mu^{\mathrm{abxx}}(\omega)\cos^{2}(\alpha) + 
\mu^{\mathrm{abyy}}(\omega)\sin^{2}(\alpha) + 
\mu^{\mathrm{abxy}}(\omega)\sin(2\alpha)}
{\xi^{\mathrm{xx}}(\omega)\cos^{2}(\alpha) + 
\xi^{\mathrm{yy}}(\omega)\sin^{2}(\alpha)}.
\label{eq:vab}
\end{align}
\end{widetext}

@@

\subsection{Layer-by-layer analysis.}\label{sec:theory-layer}

@@

@@

Using the ABINIT code \cite{gonzeCPC09} we calculated the self-consistent ground
state and the Kohn-Sham states using density functional theory in the local
density approximation (DFT-LDA) with a planewave basis. We used Hartwigsen-
Goedecker-Hutter (HGH) relativistic separable dual-space Gaussian
pseudopotentials \cite{hartwigsenPRB98} including the spin-orbit interaction
needed to calculate $\mu^{\mathrm{abcd}}(\omega)$ (Eq.
\eqref{eq:mu}) and $|\mathcal{V}^{\mathrm{a}}(\omega)|$ (Eq. \eqref{eq:vab}).
%
It is known that using DFT-LDA to calculate the electronic structure of
materials predict a different band gap than the obtained experimentally. A
correction for the band gap energy value can be calculated by other \emph{ab-
initio} methods such as the GW approximation \cite{onidaRMP02} but this is
outside the scope of this paper.
% 
The convergence parameters for the calculations of our results corresponding to
the \emph{alt} and \emph{up} structures are cutoff energies of 65\,Ha and
40\,Ha, respectively. The energy eigenvalues and matrix elements were calculated
using 14452 $\mathbf{k}$ points and 8452 $\mathbf{k}$ points in the irreducible
Brillouin zone (IBZ) and present LDA energy band gaps of 0.72\,eV and 0.088\,eV,
respectively for the \emph{alt} and \emph{up} structures.

@@

@@

\caption{Comparison of the reported maxima values of
$\mathcal{V}^{\mathrm{ab}}$ for different structures and the corresponding
polarization angle $\alpha$ and energy values.}
\label{tab:vab-str-comp}
\end{table}

@@

In figure \ref{fig:vab-str-comp} we present a comparison of the most intense
responses resulting from evaluate the Eq. \eqref{eq:vab} for the \emph{alt} and
\emph{up} 2D structures vs. CdSe and GaAs bulk structures. As we can see from
this figure the most intense response corresponds to the \emph{up} structure
centered at 0.088\,eV corresponding to the THz radiation and reaching a
spin velocity of 87.16\,Km/s.
% 
In the other hand, for an energy range from 0.66\,eV to 3.0\,eV, corresponding
to energies of the Thz and visible radiation, all the four structures have
contributions in the same order of magnitude.
% 
Starting with the 2D structures we have that the \emph{up} structure has other
two peaks centered at 1.94\,eV and 1.97\,eV reaching spin velocities of
22.2\,Km/s and -29.7\,Km/s, respectively, and the \emph{alt} structure has two
peaks centered at 0.72\,eV and 0.91\,eV reaching spin velocities of -40.2\,Km/s
and -32.9\,Km/s, respectively.
% 
Then, for the bulk structures we have that the CdSe has only one intense
response centered at 0.91\,eV reaching a spin velocity of -26.9\,Km/s, and the
GaAs structure has a large and almost planar zone where the response is held
reaching the maximum for an incoming beam of energy of 2.31\,eV and reaching a
spin velocity of -21.6\,Km/s.
% 
In table \ref{tab:vab-str-comp} we present the comparison of this values for the
2D and bulk structures.
%

@@

    \caption{$|\mathcal{V}_{\sigma^{\mathrm{z}}}|(\omega)$, response
    vs. photon energy vs. polarization angle $\alpha$ for the \emph{up}
    structure for two energy ranges. The absolute maxima is located for an
    energy range from 0.08\,eV to 0.10\,eV and the local maximum from 1.95\,eV
    to 2.0\,eV and both for polarization angles between $25^{\circ}$ and
    $50^{\circ}$.}
    \label{fig:up-3d-vsz}
\end{figure}

\begin{figure}[t]
    \centering
    \subfigure[\, \label{fig:up-vaz-rag-1}]
    {\includegraphics[width=\linewidth]{upplots/up-vaz-rag-1}}
    \\
    \subfigure[\, \label{fig:up-vaz-rag-2}]
    {\includegraphics[width=\linewidth]{upplots/up-vaz-rag-2}}

    \caption{Most intense response of
    $|\mathcal{V}_{\sigma^{\mathrm{z}}}|(\omega)$ (top frames, right scale of
    figs (a) and (b)), the corresponding velocity angle
    $\gamma_{\mathrm{z}}(\omega)$ (top frames, right scale), the collinear
    (circled box) and perpendicular (square box) angles, and the two components
    $\mathcal{V}^{\mathrm{xz}}(\omega)$ and $\mathcal{V}^{\mathrm{yz}}(\omega)$
    (bottom frames) for the \emph{up} structure fixing the energy to 0.088\,eV.
    }
    \label{fig:up-vaz-rag}
\end{figure}

% %%%%%%%%%%%%%%%%%
% %% 0.0 eV - 0.16 eV  &  1.80 ev - 2.1 ev
% %% Description of UP |V_{s^z}| 3D
% %%%%%%%%%%%%%%%%%
\textbf{Up structure}

We first present two energy ranges for the \emph{up} structure, the first for an
incoming energy beam from 0.0\,eV to 0.2\,eV in the THz radiation range where
the absolute maximum of the $|\mathcal{V}_{\sigma^{\mathrm{z}}}|(\omega)$
response is obtained and the second for an energy range from 1.80\,eV to 2.1\,eV
where two local maxima are found.
In Fig. \ref{fig:up-3d-vsz} we present the
$|\mathcal{V}_{\sigma^{\mathrm{z}}}|(\omega)$ spectra resulting from evaluate
the Eq. \eqref{eq:vs-mag} using different polarization angles $\alpha$ in the
Eq. \eqref{eq:vab} for the \emph{up} structure. In the figure we have that the
onset of the response starts when the energy of the incoming beam is the same of
the gap energy.
From this figure we obtained that the zone where the maximum response is held
corresponds to a energy range of the incident beam from 0.084\,eV to 0.093\,eV,
corresponding to the THz radiation, and polarization angles $\alpha$ between
$30^{\circ}$ and $45^{\circ}$. Also two local maxima are held for same
polarization angles but for an energy range of the incoming beam between
1.90\,eV and 2.05\,eV corresponding to the THz and visible radiation.
% %% 0.0 eV - 0.16 eV
% %% Description of UP |V_{s^z}| & gamma  vs. alpha agle
In the top frames of Figs.\ref{fig:up-vaz-rag-1} and \ref{fig:up-vaz-rag-2} we
present in solid lines the result of evaluate
$|\mathcal{V}_{\sigma^{\mathrm{z}}}|(\omega)$, related to the left scale, fixing
the energy of the incoming beam to 0.088\,eV and 0.912\,eV, respectively, for
which value the response is maximized for the \emph{up} structure. In the same
figures and frames we present in dashed lines, related to the right scale, the
corresponding velocity angle $\gamma_{\mathrm{z}}(\omega)$ obtained from the
evaluation of Eq. \eqref{eq:gamma-ang}, and in the bottom frames of those
figures the corresponding components $\mathcal{V}^{\mathrm{xz}}(\omega)$ and
$\mathcal{V}^{\mathrm{yz}}(\omega)$. Also we present two circled and square
boxes indicating the values where the angles of the spin velocity are parallel
and perpendicular and the the arrows are directed to the value of the response
corresponding to those angles.
From Figs. \ref{fig:up-vaz-rag-1} and \ref{fig:up-3d-vsz-1} we have that the
absolute maximum response for the \emph{up} structure is obtained for an
incoming beam with energy of 0.088\,eV and polarization angle
$\alpha=40^{\circ}$ resulting in a value of
$|\mathcal{V}_{\sigma^{\mathrm{z}}}|(\omega)=37.4$\,Km/s coming from the
contribution of the components $\mathcal{V}^{\mathrm{xz}}(\omega)=39.8$\,Km/s
and $\mathcal{V}^{\mathrm{yz}}(\omega)=87.2$\,Km/s for the spin polarized in the
$\mathrm{z}$ direction and having a velocity angle
$\gamma_{\mathrm{z}}(\omega)=65^{\circ}$ on the $xy$ plane.
In the same figure the green circled box indicates the value for which the
polarization angle $\alpha$ and the response direction angle
$\gamma_{\mathrm{z}}(\omega)$ are collinear being this angle $65.5^{\circ}$
resulting in a value of the response of
$|\mathcal{V}_{\sigma^{\mathrm{z}}}|(\omega)=82.3$\,Km/s indicated by the upward
green arrow.
Also the blue square box indicates the value for which the polarization angle
and the response angle are perpendicular being $\alpha=155.5^{\circ}$ and
$\gamma_{\mathrm{x}}(\omega)=65.5^{\circ}$; for this angles the response has a
value of $|\mathcal{V}_{\sigma^{\mathrm{z}}}|(\omega)=24.8$\,Km/s indicated by
the blue downward arrow.
The green and blue error bars are fixed for a value of $\pm0.5^{\circ}$ and
then, for this variation in the $\gamma_{\mathrm{z}}(\omega)$ angle the complete
range of $\alpha$ angle is included because this last is almost constant.
Now from Figs. \ref{fig:up-vaz-rag-2} and \ref{fig:up-3d-vsz-2} we have that a
local maxima of the response is obtained for an incoming beam with energy of
0.912\,eV and same polarization angle $\alpha=40^{\circ}$ resulting in a value
of $|\mathcal{V}_{\sigma^{\mathrm{z}}}|(\omega)=30.3$\,Km/s directed in a
velocity angle $\gamma_{\mathrm{z}}(\omega)=78^{\circ}$ on the $xy$ plane for
the spin polarized in the $z$ direction.
Again the green circled box indicates the value for which the polarization angle
$\alpha$ and the response direction angle $\gamma_{\mathrm{z}}(\omega)$ are
collinear being both $78.5^{\circ}$ and having a response value of
$|\mathcal{V}_{\sigma^{\mathrm{z}}}|(\omega)=23.5$\,Km/s indicated with the
green upward arrow. We found that for variations in the response angle of $\pm
2^{\circ}$, indicated with the error bars, corresponds a range in the
polarization angle of $0^{\circ} \leq \alpha \leq 122^{\circ}$ having then a
large range for which the direction of the response is directed to this angle.
The blue square box indicates the value for which the polarization angle and the
response angle are perpendicular being $\alpha=168.5^{\circ}$
$\gamma_{\mathrm{z}}(\omega)=78.5^{\circ}$ and having a response
$|\mathcal{V}_{\sigma^{\mathrm{z}}}|(\omega)=9.0$\,Km/s indicated with the blue
upward arrow. Again, for variations in the response angle of $\pm2^{\circ}$,
indicated with the error bars, corresponds a range in the polarization angle of
$155^{\circ} \leq \alpha \leq 180^{\circ}$ having again a large range for which
the direction of the response is held.

@@

\begin{figure}[tb]
    \centering
    \includegraphics[width=\linewidth]{altplots/alt-3d-svaz}
    \caption{$|\mathcal{V}_{\sigma^{\mathrm{z}}}|(\omega)$, response
    vs. photon energy vs. polarization angle $\alpha$ for the \emph{alt}
    structure. The absolute maximum is located for an energy range from 0.90\,eV
    to 0.93\,eV and for polarization angles between $120^{\circ}$ and
    $150^{\circ}$.}
    \label{fig:alt-3d-vsb}
\end{figure}

\begin{figure}[t]
    \centering
    \includegraphics[width=\linewidth]{altplots/alt-vaz-rag}
    \caption{Most intense response of
    $|\mathcal{V}_{\sigma^{\mathrm{z}}}|(\omega)$ (top frame, left scale) the
    corresponding velocity angle $\gamma_{\mathrm{z}}(\omega)$ (top frame, right
    scale), the collinear (circled box) and perpendicular (square box) angles,
    and the two components $\mathcal{V}^{\mathrm{xz}}(\omega)$ and
    $\mathcal{V}^{\mathrm{yz}}(\omega)$ (bottom frame) for the \emph{alt}
    structure fixing the energy to 0.912\,eV.}
    \label{fig:alt-vaz-rag}
\end{figure}

% %%%%%%%%%%%%%%%%%
% %% 0.0 eV - 0.16 eV  &  1.80 ev - 2.1 ev
% %% Description of ALT |V_{s^z}| 3D
% %%%%%%%%%%%%%%%%%
\textbf{Alt structure}

In Fig. \ref{fig:alt-3d-vsb} we present the
$|\mathcal{V}_{\sigma^{\mathrm{z}}}|(\omega)$ spectra resulting from evaluate
again the Eq. \eqref{eq:vs-mag} vs. the photon energy of the incident beam vs.
the polarization angle $\alpha$ in Eq. \eqref{eq:vab} for the \emph{alt}
structure . In the figure we have that the onset of the response starts when the
energy of the incoming beam is the same of the gap energy.
% 
From this figure we found that the zone where the absolute maximum response is
held corresponds to a energy range from 0.90\,eV to 0.93\,eV, corresponding to
the THz raduation, and polarization angles $\alpha$ between $120^{\circ}$ and
$150^{\circ}$. Also, a local maximum is obtained for the same polarization
angles but for energies between 0.67\,eV and 0.75\,eV.
% 
% %%%%%%%%%%%%%%%%%
% %% 0.0 eV - 0.16 eV
% %% Description of ALT |V_{s^z}| & gamma  vs. alpha agle
% %%%%%%%%%%%%%%%%%
In the top frame of Fig. \ref{fig:alt-vaz-rag} we present in solid line the
result of evaluate $|\mathcal{V}_{\sigma^{\mathrm{z}}}|(\omega)$, related to the
left scale, fixing the energy of the incoming beam to 0.912\,eV for which value
the response is maximized for the \emph{alt} structure. In the same figure and
frame we present in dashed line, related to the right scale, the velocity angle
$\gamma_{\mathrm{z}}(\omega)$ and in the bottom frame the corresponding
$\mathcal{V}^{\mathrm{xz}}(\omega)$ and $\mathcal{V}^{\mathrm{yz}}(\omega)$
components. Again, the circled and square boxes indicate the values for which
the polarization angle and the velocity angle are parallel and perpendicular and
with arrows are indicated the corresponding response value.
% 
From this figure and from Fig. \ref{fig:alt-3d-vsb} we have that the absolute
maximum response for the \emph{alt} structure is obtained for an incoming beam
with polarization angle $\alpha=145^{\circ}$ reaching a velocity of
$|\mathcal{V}_{\sigma^{\mathrm{z}}}|(\omega)=43.0$\,Km/s and for the spin
polarized in the $\mathrm{z}$ direction and resulting in a velocity angle
$\gamma_{\mathrm{z}}(\omega)=50^{\circ}$ on the $xy$ plane. The circled box for
the collinear angle corresponds for angles $\alpha$ and
$\gamma_{\mathrm{z}}(\omega)$ equal to $53.5^{\circ}$ with a value of
$|\mathcal{V}_{\sigma^{\mathrm{z}}}|(\omega)=12.7$\,Km/s, and the blue square
box indicates the perpendicular angles for values $\alpha=140^{\circ}$ and
$\gamma_{\mathrm{z}}(\omega)=50^{\circ}$ with a value of
$|\mathcal{V}_{\sigma^{\mathrm{z}}}|(\omega)=43$\,Km/s. Finally we found that
for variations of $\pm0.5^{\circ}$ of those collinear and perpendicular angles,
presented with the error bars on the boxes, correspond ranges for the
polarization angle $30^{\circ} \leq \alpha \leq 70^{\circ}$ and $95^{\circ} \leq
\alpha \leq 175^{\circ}$ because the response angle
$\gamma_{\mathrm{z}}(\omega)$ has small variations for the complete range of the
polarization angle $\alpha$.

@@

\textbf{Up structure.}
\begin{figure}[t]
    \centering
    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|(\omega)$ for \emph{up} structure
    \label{fig:up-3d-vvx-1}]
    {\includegraphics[width=\linewidth]{upplots/up-3d-vxb-1}}
    \\
    \subfigure[\ $|\mathcal{V}^{\mathrm{y}}|(\omega)$ for \emph{up} structure
    \label{fig:up-3d-vvy-1}]
    {\includegraphics[width=\linewidth]{upplots/up-3d-vyb-1}}

@@

% %%%%%%%%%%%%%%%%%
% %% 0.0 eV - 0.16 eV
% %% Description of UP |V^{a}| 3D
% %%%%%%%%%%%%%%%%%
For the \emph{up} structure we first analyzed the energy range from 0.00\,eV to
0.16\,eV, where we found the most intense response and the absolute maxima for
$|\mathcal{V}^{\mathrm{x}}|(\omega)$ and $|\mathcal{V}^{\mathrm{y}}|(\omega)$.
% 
In Fig. \ref{fig:up-3d-vva-1} we present the
$|\mathcal{V}^{\mathrm{a}}|(\omega)$ spectra resulting from evaluate the Eq.
\eqref{eq:vv-mag} using different polarization angles $\alpha$ in the Eq.
\eqref{eq:vab} for the \emph{up} structure. We can see that the onset of the
response is when the energy of the incoming light is the same of the gap energy.
%
From this picture we can see that for the zone between the energy range of
0.084\,eV-0.093\,eV,corresponding to the THz radiation, and polarization angles
between $30^{\circ}$ and $45^{\circ}$ is the zone where the maximum response is
held for both, $|\mathcal{V}^{\mathrm{x}}|(\omega)$ and
$|\mathcal{V}^{\mathrm{y}}|(\omega)$.
% %%%%%%%%%%%%%%%%%
% %% 1.8 eV - 2.0 eV
% %% Description of UP |V^{a}|, components and RTP
% %%%%%%%%%%%%%%%%%

@@

@@

@@

1.80\,eV to 2.10\,eV, corresponding to the THz and visible radiation, presented
in Fig. \ref{fig:up-3d-vva-2} where two local maxima of
are obtained for the \emph{up} structure.

@@

@@

\textbf{Alt structure.}
\begin{figure}[tb]
    \centering
    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|$ for \emph{alt} structure 
    \label{fig:alt-3d-vvx}]
    {\includegraphics[width=\linewidth]{altplots/alt-3d-vxb}}
    \\
    \subfigure[\ $|\mathcal{V}^{\mathrm{y}}|$ for \emph{alt} structure 
    \label{fig:alt-3d-vvy}]
    {\includegraphics[width=\linewidth]{altplots/alt-3d-vyb}}

@@

% %% Description of ALT |V^{a}| 3D

@@

1.0\,eV, corresponding to the THz radiation, where we found the a local maxima
and the most intense responses for $|\mathcal{V}^{\mathrm{x}}|(\omega)$ and
$|\mathcal{V}^{\mathrm{a}}|(\omega)$. In Fig. \ref{fig:alt-3d-vva} we present
the $|\mathcal{V}^{\mathrm{a}}|(\omega)$ spectra resulting from evaluate again
Eq. \eqref{eq:vv-mag} using different polarization angles $\alpha$ in Eq.
